%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {AccuKnox}{Aug 2022 -- Present}
    {Software Engineer}{Remote, India}
    \resumeItemListStart
        % \resumeItem{Implemented microservices architecture using Node.js and Express, improving API response time by 25\% and reducing server load by 30\%.}
        % \resumeItem{Led a cross-functional team in implementing a new feature using React and Redux, resulting in a 20\% increase in user engagement within the first month.}
        % \resumeItem{Optimized MySQL database queries, reducing page load times by 15\% and enhancing overall application performance.}
        % \resumeItem{Developed and maintained a \textbf{registry scanning} system using \textbf{Kubernetes} jobs and a microservice. The microservice manages registry operations via APIs, while the Kubernetes jobs handle image analysis and scanning across multiple registries.}
        % \resumeItem{Developed a \textbf{gRPC} gateway to connect agents with our platform, reducing data transmission latency by over \textbf{95\%} and improving setup efficiency and security compared to the previous Pulsar-based system.}
        \resumeItem{\textbf{Built} and \textbf{managed} a registry scanning system with \textbf{Kubernetes} jobs and a \textbf{microservice}, where the microservice handles registry operations via \textbf{APIs}, and the Kubernetes jobs perform image analysis and scanning across 10+ registry providers.}
        \resumeItem{Created a \textbf{gRPC} gateway to link agents with our platform, \textbf{cutting} data transmission latency by over \textbf{90\%} and boosting setup efficiency and security compared to the previous Pulsar system.}
        \resumeItem{\textbf{Engineered} an \textbf{adapter} library to facilitate seamless integration with 2+ message queues, vault, and 2+ database engines, providing a unified interface for easier connectivity.}
        \resumeItem{Managed Channel Integration, streamlining the delivery of notifications from our SaaS platform to various systems. Refactored the codebase and \textbf{optimized} sql queries, boosting \textbf{response} times by \textbf{50\%} and enhancing overall system performance.}
        \resumeItem{Contributed to software \textbf{releases} and service \textbf{deployments}, ensuring smooth and efficient rollouts.}
        \resumeItem{\textbf{Reviewed} peer \textbf{pull requests} to provide initial quality checks and ensure coding standards.}
    \resumeItemListEnd
    
    \resumeSubheading
    {KloudOne}{Nov 2021 -- July 2022}
    {Software Engineer Trainee}{Remote, India}
    \resumeItemListStart
        \resumeItem{Created a GitHub bot to automatically merge or close pull requests based on specific conditions..}
        \resumeItem{Migrated multiple microservices from \textbf{MySQL} to \textbf{PostgreSQL}, updating raw SQL queries to \textbf{GORM}.}
        \resumeItem{Developed multiple internal packages to reduce code duplication and enhance maintainability across microservices. \textbf{Upgraded Go version} in multiple services.}
    \resumeItemListEnd

\resumeSubHeadingListEnd