%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{ClickCart} $|$ \emph{Golang, Gin, MongoDB, JWT}}    {}
    % {\textbf{ClickCart} $|$ \emph{Golang, Gin, MongoDB, JWT, Flask, Ruby on Rails}}    {}
    \resumeItemListStart
        \resumeItem {Developed an e-commerce server with JWT-based authentication, handling over 100 user accounts.}
        \resumeItem{Implemented role-based access with three distinct roles:}
        \resumeItemListStart
            \resumeItem{\textbf{Viewer}: View products and add items to cart.}
            \resumeItem{\textbf{Master}: Manage and edit their products and project details.}
            \resumeItem{\textbf{Admin}: Full administrative control, including user and product management.}
         \resumeItemListEnd
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Smart Parking System} $|$ \emph{Golang, Mux, SQLite}}{}
    \resumeItemListStart
        \resumeItem{Developed a smart parking system with automatic \textbf{transaction} records, receipt generation, and sms alerts via SQL.}
        % \resumeItem{Created a \textbf{Dockerfile} and set up a CI/CD pipeline for automated builds and image push to \textbf{DockerHub}.}
        \resumeItem{Engineered a robust \textbf{Dockerfile} and established a CI/CD pipeline for seamless automated builds, significantly reducing deployment time by \textbf{60\%} and enabling releases to DockerHub without manual intervention.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Realtime Chat Application} $|$ \emph{Golang, Websocket, React}}{}
    \resumeItemListStart
        \resumeItem{\textbf{Built} a real-time chat app for multiple users, implemented \textbf{WebSocket} for \textbf{instant} communication.}
        \resumeItem{\textbf{Designed} a user-friendly frontend with React. Developed a scalable backend using Golang.}
    \resumeItemListEnd

\resumeSubHeadingListEnd